Place of death in NRS COVID-19 deaths

### 2021-02-25 covid_nrs_place_of_death.Rmd
Changed to use calibri font, but broken most outputs in process. fix display of pdfs! (by embedding calibri font, I assume?)

```{r}
areas_relatively_higher_number_home_deaths_text <- "Lighter areas represent areas with relatively higher number of home deaths in 2020 compared to historical mean"
home_deaths_ratio_text_text <- "Ratio computed from total home deaths in 2020 divided by mean annual home deaths 2015-2019"

>>>>

```{r}
areas_relatively_higher_number_home_deaths_text <- "Lighter areas represent areas with relatively higher number of home deaths in 2020 compared to historical mean"
home_deaths_ratio_text <- "Ratio computed from total home deaths in 2020 divided by mean annual home deaths 2015-2019"
